One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
edited the Navigation section

There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the center providing the computing resources.
For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learner everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.

@@

 %---> ? \cite{epstein2002immediate}.

@@

\subsection{Navigation}\kh{Vorschlag Unterkapitel in "Results" umbenennen oder an anderer Stelle aus "Erwartungsgründen" ein "Results"-Kapitel ergänzen (am besten natürlich auf der Hauptgliederungsebene, aber das wird vermutlich schwierig werden)}
%\paragraph{Navigation}
Thanks to the contributions of the PeCoH project, a JavaScript prototype enables the embedding of a navigable skill tree into a webpage.
The script can be used by different stackholders to present their own view on the skill-tree.
By view we mean the selection and organization of the skills, and the additional information provided when navigating the tree.
For instance, you could have a tree for a specific scientific domain, for a specific data center, or even for the role of the tester of a specific application; it could indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.

>>>>

There is a generally accepted set of skills and competencies necessary to efficiently use HPC resources.
This skill set depends on the role and domain of the practitioner but also on the available infrastructure of the centre providing the computing resources.
For example, a scientist needing to run an application on a specific machine may need basic skills in Linux, MPI, environment modules, and knowledge about the batch scheduler, e.g., Slurm.
Now rather than providing that scientists with a list of instructions to be followed in a copy and paste fashion or a never-ending list of things they should know, we want them to understand each of the required steps without having to learner everything about it, but at the same time understand how it fits into the bigger picture of using an HPC system.
For instance, understanding Slurm is a good example of a very fine-grained skill that fits under a more generic skill defined as "resource management", illustrating concepts across the rich variety of available resource managers.

@@

 %---> ? \cite{epstein2002immediate}. Not sure this still fits here [WF]

@@

\subsection{Navigation}\kh{Vorschlag Unterkapitel in "Results" umbenennen oder an anderer Stelle aus "Erwartungsgründen" ein "Results"-Kapitel ergänzen (am besten natürlich auf der Hauptgliederungsebene, aber das wird vermutlich schwierig werden)}
%\paragraph{Navigation}
Thanks to the contributions of the PeCoH project, a JavaScript prototype embeds a navigable skill tree into a webpage.
The script can be used by different stakeholders to adjust and present the skill tree in the most suitable for them view.
By view we mean the selection and organisation of the skills, and the additional information provided when looking at the tree.
For instance, you could have a tree for a specific scientific domain, for a specific data centre, or even for the role of the tester of a specific application. 
This feature could be used to indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.
